### 2014-06-24 tex/intro.tex
Added

\newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}

@@

Lazy initialization is a symbolic execution technique where memory structures are created on-demand, as they are required.

>>>>

In recent years symbolic execution --
a program analysis technique for systematic exploration of
program execution paths using symbolic input values -- has provided
the basis for many software testing and analysis techniques.
For each execution path explored during symbolic execution, constraints
on the symbolic inputs are collected to create a \emph{path
condition}. The set of path conditions computed by symbolic execution
characterize the observed program execution behaviours and can
be used to perform various analyses of program behavior, e.g.,
regression testing~\cite{} and differential program 
analysis~\cite{}.

Initial work on symbolic execution largely focused on checking 
properties of programs with primitive types, such as integers and 
booleans~\cite{clarke76TSE,King:76}. With the advent of object-oriented
languages, such as Java and C$++$, one of the fundamental challenges 
of using symbolic execution for program analysis
has been how to analyze programs containing
complex data structures with unbounded domains, i.e., data stored
on the heap. State-of-the-art symbolic execution techniques have 
addressed this challenge by constructing the heap in a lazy manner, 
deferring materialization of objects on the concrete heap until
they are needed, i.e., until execution of a statement with a 
dereference expression ($x = r.f$)~\cite{Kiasan06,Kiasan07,GSE03}.

Although the lazy symbolic execution techniques have been instrumental 
in enabling analysis of heap manipulating software, treatment of
heap data follows concrete program semantics once a heap location is
materialized. The effect is to exacerbate 
the state space explosion problem by creating additional points of 
non-determinism during symbolic execution to account for the 
different possible concrete heap configurations.

Need a transition here to talk about a symbolic heap

In this paper we present a novel approach to lazy symbolic
execution....

Our technique is 1) scalable -- it constructs the symbolic
heap on-the-fly during symbolic execution but avoids introducing 
additional points of non-determinism
by maintaining only a (fully) symbolic heap,
2) precise -- at any given point during symbolic execution, 
the symbolic heap represents the exact set of feasible
concrete heap structures for the program under analysis, and
3) expressive -- the symbolic heap can represent recursive data structures 
and heaps resulting from loops and recursive control structures in the code. 
We report on a case-study of an implementation of our technique in the
Symbolic PathFinder tool to illustrate
 its scalability and we discuss how test case generation -- a common
 use for the results of symbolic execution -- can benefit from symbolic
 execution using a fully symbolic heap.

This paper makes the following contributions:

\begin{itemize}
\item{We present a novel technique for analyzing heap manipulating
programs that constructs a fully symbolic representatino of
the heap on-the-fly durig symbolic execution.}
\item{We prove the soundness and completeness of our algorithm...}
\item{We implement our approach in the Symbolic PathFinder tool}
\item{We demonstrate experimentally that our technique improves
the scalability of symbolic execution of heap maninpulating software
over state-of-the-art techniques.}

 \end{itemize}

\begin{comment}
\newcommand{\Indstate}[1][1]{\State\hspace{#1\algorithmicindent}}

@@

Lazy initialization is a symbolic execution technique where memory structures are created on-demand, as they are required.
\end{comment}
